Improving Multi-Domain Neural Machine Translation with Differential Data Selection

### 2021-05-05 2021/emnlp/mdmt.tex
petits changements

\begin{table*}
  \centering \small
  \begin{tabular}{|l|*8{r|}} \hline
    domain \hfill $d=$ & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{mean} \\ \hline
    FT-Full($d$) \hfill [BLEU] &37.7&59.2&54.5&34&46.8&90.8&53.8\\
    FT-Res($d$) \hfill &37.3&57.9&53.9&33.8&46.7&90.2&53.3\\ \hline
    \hline
    \system{DDS($\vlambda_0, \vlambda_d$)} \hfill [BLEU] &36.7&56.2&54.3&33.5&46.8&91.8&53.2\\
    \% domain $d$ (final / total) & 59.7 / 49.5 & 6.5 / 18.3 & 14.9 / 24.5 & 6.4 / 12.8 & 67.2/47.4 & 67.2 / 45.3&\\ \hline
    \system{DDS($\vlambda_1, \vlambda_d$)} \hfill [BLEU]&36.4&56.3& 45.4& 32.6&44.5&43.1&43.1\\
    \% domain $d$& 89 / 86.6 & 50/18.4 & 1.4 / 1.6 & 3.0 / 2.5 & 7.5 / 9.2 & 1.0 / 1.0 \\ \hline
    \system{CL($d$)} \hfill [BLEU]&  \\ 
    \% domain $d$& \\ \hline\hline
    % Multidomain
    \system{Mixed-0}      & 35.3 & 54.1 & 52.5 & 31.9 & 44.9 & 89.5& 51.4 \\
    \system{Mixed-0.25} & 35.9 & 54.9 & 52.6 & 32.6 & 45 & 90.3& 51.9 \\
    \system{Mixed-0.5}   & 36.1 & 55.4 & 51.8 & 33.5 & 46.2 & 90 & 52.2 \\
    \system{Mixed-0.75} & 36.5 & 55 & 51.2 & 34 & 44.3 & 87.2& 51.7 \\
    \system{Mixed-1}     & 37.3  & 54.6 & 50.1 & 33.5 & 43.2 & 77.5& 49.4 \\
    \system{MDL-Res} &37.1&57.4&53.6&33.2&46&90.7&53\\\hline
    \system{DDS($\vlambda_1, \vlambda_0$)} &37.9&50.2&47.2&31.2&40.8&58.6&44.3\\
    $\operatorname{KL}(\vlambda_*^{l}, \vlambda_0$) &37&55.6&52.9&33.1&44.5&91.3&52.4 \\
%    $ \mathcal{H}(\vlambda_*^{l})$ &  \\
    \system{DDS($\vlambda_0, \vlambda_0$)} &37.3&55.1&51&33.5&43.4&90.8&51.8\\ \hline
  \end{tabular}
  \caption{Baseline results for DDS in fine-tuning and multi-domain adaptation. In the top part, we report scores with DDS and each target domain, and compare with full-fine-tuning: each column corresponds to a different system. We also report the proportion of in-domain data in the final mixture. In the bottom part, we run multi-domain experiments: for a given line, all the columns \emph{correspond to the same system}. We also report the KL divergence between the optimal and the target mixtures.}
  \label{tab:basic-dds}
\end{table*}

@@

\subsection{Unsupervised DDS}
To better analyze the behavior of DDS, we study a scenario where $\vlambda^s$ and $\vlambda^t$ have different dimensions designed as follows. All training data is automatically clustered into $K=30$ of varying sizes using the k-means algorithm based on generic sentence representations obtained via mean pooling. The resulting classes contain from a tenths of thousands to several hundreds of thousand training samples. Most classes contain a dominant domain, which accounts for more of 90\% of the samples.\footnote{See detail in supplementary material} Using the same DA setting as before, we study (a) whether DDS is able to identify the classes that correspond to the domain of interest (b) whether having additional degrees of freedom can yield an improved training performance (c) how DDS scales when a large number of  domains is considered.\fyTodo{TBC - with what experiments?}

@@

This idea is reminiscent of the work of \citet{alex17automated} and  \citet{Kumar19reinforcement}, who also design their curriculum trainng strategy based on the development loss.

>>>>

\begin{table*}
  \centering \small
  \begin{tabular}{|l|*8{r|}} \hline
    domain \hfill $d=$ & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{mean} \\ \hline
    FT-Full($d$) \hfill [BLEU] &37.7&59.2&54.5&34&46.8&90.8&53.8\\
    FT-Res($d$) \hfill &37.3&57.9&53.9&33.8&46.7&90.2&53.3\\ \hline
    \hline
    \system{DDS($\vlambda_0, \vlambda_d$)} \hfill [BLEU] &36.7&56.2&54.3&33.5&46.8&91.8&53.2\\
    \% domain $d$ (final / total) & 59.7 / 49.5 & 6.5 / 18.3 & 14.9 / 24.5 & 6.4 / 12.8 & 67.2/47.4 & 67.2 / 45.3&\\ \hline
    \system{DDS($\vlambda_1, \vlambda_d$)} \hfill [BLEU]&36.4&56.3& 45.4& 32.6&44.5&43.1&43.1\\
    \% domain $d$& 89 / 86.6 & 50/18.4 & 1.4 / 1.6 & 3.0 / 2.5 & 7.5 / 9.2 & 1.0 / 1.0 \\ \hline
    \system{CL($d$)} \hfill [BLEU]&  \\ 
    \% domain $d$& \\ \hline\hline
    % Multidomain
    \system{Mixed-0}      & 35.3 & 54.1 & 52.5 & 31.9 & 44.9 & 89.5& 51.4 \\
    \system{Mixed-0.25} & 35.9 & 54.9 & 52.6 & 32.6 & 45 & 90.3& 51.9 \\
    \system{Mixed-0.5}   & 36.1 & 55.4 & 51.8 & 33.5 & 46.2 & 90 & 52.2 \\
    \system{Mixed-0.75} & 36.5 & 55 & 51.2 & 34 & 44.3 & 87.2& 51.7 \\
    \system{Mixed-1}     & 37.3  & 54.6 & 50.1 & 33.5 & 43.2 & 77.5& 49.4 \\
    \system{MDL-Res} &37.1&57.4&53.6&33.2&46&90.7&53\\\hline
    \system{DDS($\vlambda_1, \vlambda_0$)} &37.9&50.2&47.2&31.2&40.8&58.6&44.3\\
    $\operatorname{KL}(\vlambda_*^{l}, \vlambda_0$) &37&55.6&52.9&33.1&44.5&91.3&52.4 \\
%    $ \mathcal{H}(\vlambda_*^{l})$ &  \\
    \system{DDS($\vlambda_0, \vlambda_0$)} &37.3&55.1&51&33.5&43.4&90.8&51.8\\ \hline
  \end{tabular}
  \caption{Baseline results for DDS in fine-tuning and multi-domain adaptation. In the top part, we report scores with DDS and each target domain, and compare with full fine-tuning: each column corresponds to a distinct system. We also report the proportion of in-domain data in the final mixture. In the bottom part, we run multi-domain experiments: for a given line, all the columns \emph{correspond to the same system}. We also report the KL divergence between the optimal and the target mixtures.}
  \label{tab:basic-dds}
\end{table*}
\fyTodo{Report CL results / explain in legend}

@@

\subsection{Unsupervised DDS}
To better analyze the behavior of DDS, we study a scenario where $\vlambda^s$ and $\vlambda^t$ have different dimensions designed as follows. All training data is automatically clustered into $K=30$ of varying sizes using the k-means algorithm based on generic sentence representations obtained via mean pooling. The resulting classes contain from a tenths of thousands to several hundreds of thousand training samples. Most classes contain a dominant domain which accounts for more of 90\% of the samples.\footnote{See detail in supplementary material} Using the same DA setting as before, we study (a) whether DDS is able to identify the classes that correspond to the domain of interest (b) whether having additional degrees of freedom\fyTodo{explain better} can yield an improved training performance (c) how DDS scales when a large number of  domains is considered.\fyTodo{TBC - with what experiments?}

@@

This idea is reminiscent of the work of \citet{Graves17automated} and \citet{Kumar19reinforcement}, who also design their curriculum trainng strategy based on the development loss.
